Plug-and-Play Dual-Tree Algorithm Runtime Analysis

### 2015-12-28 bounds-files/sec01-supporting-lemmas.tex
Use titlecase for section headings.
No parentheses in parenthetical citations.

\subsection{The cover tree}

@@

\subsection{Expansion constant}

@@

\begin{itemize}
  \item {\bf Width bound:} no cover tree node has more than $c^4$ children
(Lemma 4.1, \cite{langford2006}).

  \item {\bf Depth bound:} the maximum depth of any node is $O(c^2 \log N)$
(Lemma 4.3, \cite{langford2006}).

  \item {\bf Space bound:} a cover tree has $O(N)$ nodes (Theorem 1,
\cite{langford2006}).
\end{itemize}

>>>>

\subsection{The Cover Tree}

@@

\subsection{Expansion Constant}

@@

\begin{itemize}
  \item {\bf Width bound:} no cover tree node has more than $c^4$ children
(Lemma 4.1, \citealp{langford2006}).

  \item {\bf Depth bound:} the maximum depth of any node is $O(c^2 \log N)$
(Lemma 4.3, \citealp{langford2006}).

  \item {\bf Space bound:} a cover tree has $O(N)$ nodes (Theorem 1,
\citealp{langford2006}).
\end{itemize}
